### 2015-11-12 AssignmentV/Assignment5-Ditz_Schroeder-WS15-16.tex
ein paar weitere "verbesserungen" für die erste aufgabe

General we are now only looking at the worst case scenario, which means uniform distributed mistmatches in an alignment. Also we only look at $k>=1$, as $k=0$ is in our application not a useful result. Assume two sequences of length t with l mismatches.\\
 Than both sequences contain $l$ tuples of length $\lfloor\frac{t}{l+1}\rfloor$ and one tuple which has a length of maximal $\lfloor\frac{t}{l+1}\rfloor$ . Where $k = \lfloor\frac{t}{l+1}\rfloor$ is the maximal tuple length, possible in sequences.\\
\\
\noindent So both sequences share $l+1$ k-tuples and for each 
$k \le \lfloor\frac{t}{l+1}\rfloor$ they share $(l+1) * \lfloor\frac{\lfloor\frac{t}{l+1}\rfloor}{k}\rfloor$
k-tuples.

>>>>

General we are now only looking at the worst case scenario, which means uniform distributed mistmatches in an alignment. Also we only look at $k>=1$, as $k=0$ is in our application not a useful result. Assume two sequences of length t with l mismatches.\\
 Than both sequences contain $l$ tuples of length $L = \lfloor\frac{t}{l+1}\rfloor$ and one tuple which has a length of maximal $\lfloor\frac{t}{l+1}\rfloor$ . \\
\\
\noindent So both sequences share $l$ or $l+1$ k-tuples, if $k = \lfloor\frac{t}{l+1}\rfloor$, and for each 
$k \le \lfloor\frac{t}{l+1}\rfloor$ they share $(l+1) * \lfloor\frac{L}{k}\rfloor$
k-tuples.
